### 2017-10-10 analysis-note-vf/results.tex
update the analysis note with the latest incoherent results

\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{eqnarray}
\normalsize

Where $S{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
leptonic tensor. Their explicit expressions can be found in Appendix 
\ref{app:Helium_cross_section}.

@@

\begin{figure}[tpb]
\includegraphics[scale=0.9]{fig_Dec2016/ALU_phi_p_Q2.pdf}
\includegraphics[scale=0.9]{fig_Dec2016/ALU_phi_p_x.pdf}
\includegraphics[scale=0.9]{fig_Dec2016/ALU_phi_p_t.pdf}
\caption{The incoherent $A_{LU}$ as a function of the angle $\phi$ in $Q^2$, 
   $x_B$, and $-t$ bins, respectively from top to bottom. See the caption of 
   figure \ref{fig:bsa_coh_Q2_bins} for the color indications. The red lines 
   represent fits to the $\frac{\alpha \sin(\phi)}{1 + \beta cos(\phi)}$ 
   function.  } \label{fig:bsa_incoh_bins}
\end{figure}

>>>>

\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{eqnarray}
\normalsize

Where $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
leptonic tensor. Their explicit expressions can be found in Appendix 
\ref{app:Helium_cross_section}.

@@

\begin{figure}[tpb]
\includegraphics[scale=0.9]{fig_Dec2016/incoherent_ALU_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of the angle $\phi$ in $Q^2$, 
   $x_B$, and $-t$ bins, respectively from top to bottom. See the caption of 
   figure \ref{fig:bsa_coh_Q2_bins} for the color indications. The red lines 
   represent fits to the $\frac{\alpha \sin(\phi)}{1 + \beta cos(\phi)}$ 
function.  } \label{fig:bsa_incoh_bins}
\end{figure}
